---
title: "Prigozhin audio files, transcribed"
description: "An automatic transcription of all the audio messages posted on Prigozhin's official Telegram channel"
author: Giorgio Comai
date: 2023-08-08
last-modified: 2023-08-08
categories: [dataset, automatic transcription, Telegram, Russian language, Russian media]
---

{{< include ./../_early_disclaimer.qmd >}}

```{r setup, echo = FALSE, message=FALSE}
#library("extrafont")
knitr::opts_chunk$set(echo = FALSE,
                      fig.width = 8,
                      fig.height = 4.5)

library("ggplot2")
library("dplyr", warn.conflicts = FALSE)

ggplot2::theme_set(new = theme_minimal(base_family = "Roboto Condensed"))

audio_messages_df <- readr::read_csv(file = "prigozhin_audio_files_en.csv")

```

Prigozhin started to post audio messages on his official Telegram channel - the press service of his holding company - in late 2022. He abruptly stopped after his mutiny in late June 2023. This dataset includes an automatic transcription both in Russian and English created using the [whisper models](https://github.com/openai/whisper) (more specifically,the `large` model), through [a dedicated r package](https://github.com/bnosac/audio.whisper). Find more details and context about the process in the dedicated post.

**Read full post with more context**: "[From the 'battle of Bakhmut' to the 'march of justice': Prigozhin's audio files, transcribed](/posts/2023-08-telegram_prigozhin/)"

The same contents available here for download can more conveniently be consulted at the following pages:

-   [**Read all transcripts in English**](/posts/2023-08-telegram_prigozhin/prigozhin_transcribed_en.qmd)
-   [**Read all transcripts in Russian**](/posts/2023-08-telegram_prigozhin/prigozhin_transcribed_ru.qmd)

## Accuracy of the dataset

Contents presented here are the result of automatic transcription / translation. Transcription is mostly accurate but the spelling of names of persons or organisations is inconsistent. Automatic translation is in English is mostly usable, but inaccuracies are more frequent.

::: callout-warning
## Work-in-progress

**Not all audio messages have been transcribed yet. Currently this page shows some of the earliest and some of the most recent posts. A total of 408 audio messages will be included when the processing will be completed; this warning will then be removed.**
:::

## Summary statistics

```{r results='asis'}
cat("__Total number of posts including audio messages__: ")
cat(scales::number(nrow(audio_messages_df |> dplyr::distinct(id))))
cat("<br />")
cat("__Earliest post with audio__: ")
cat(format.Date(x = min(audio_messages_df$datetime), "%d %B %Y"))
cat("<br />")
cat("__Most recent post with audio__: ")
cat(format.Date(x = max(audio_messages_df$datetime), "%d %B %Y"))
cat("<br />")


```

## Downloads

-   Russian version: [prigozhin_audio_files_ru.csv](prigozhin_audio_files_ru.csv)
-   English version: [prigozhin_audio_files_en.csv](prigozhin_audio_files_en.csv)

### About the identifier

The `id` column included in the dataset reflects the identifier of a given post on Telegram. The original post can be seen by adding the relevant id to the base address of the Telegram channel: https://t.me/concordgroup_official/

The `id` column can hence also be used to match this dataset with export files generated by Telegram itself.
