---
title: "zavtra.ru_ru_2024"
description: "Corpus based on the website of Russian magazine 'Zavtra' (in Russian, 1996-2023)"
author: Giorgio Comai
date: 2024-04-12
last-modified: 2024-04-12
categories: ["corpus", "full corpus", "Russian media", "Russian language"]
editor: source
---


```{r setup, echo = FALSE, message=FALSE, warning=FALSE, results='asis'}
website_name <- "zavtra.ru_ru"
description_string_01 <- "all items published on"
description_string_02 <- "zavtra.ru"
license_string <- "[Creative Commons Attribution 4.0 International](https://creativecommons.org/licenses/by/4.0/deed.ru)"

source(fs::path("..", "russian_institutions_2024", "dataset_setup_2024.R"))

download_callout()
```


## Scope of this corpus

This corpus is based on the website of Russian magazine [zavtra.ru](http://zavtra.ru/). More specifically, according to the ["about" page of the website](https://zavtra.ru/about), the website zavtra.ru "appeared on the basis of the digital version of the newspaper "Zavtra".

The structure of the website - an archive with a separate issue dedicated to teach issue of the printed version of the magazine, and the respective page showing in which page of the printed version the article appears - suggests a strict correspondence between the online and the printed version; this, however, has not been checked. 

The website also hosts additional contents, such as podcasts, which are not included in this corpus. Only contents linked from the archive page of an issue of the magazine are included in this corpus. 

The earliest issue included is issue 149, published on 14 October 1996. The most recent issue included is issue 1563, published on 27 December 2023.


## Summary statistics

```{r summary_stats, results='asis'}
summary_stats_text()
```

```{r items_per_year}
items_per_year()
```

```{r words_per_year}
words_per_year()
```


```{r missing_table}
missing_table()
```

```{r missing_graph}
missing_graph()
```


## Narrative explanation of how this textual corpus was built

Zavtra keeps a full archive of its publications starting from 1996. This corpus was built through a script that retrieves archive pages for each year (e.g. [this for 1996](https://zavtra.ru/archive/1996)), then retrieves the link to the page dedicated to each issue, and from there, extracts links to individual articles. Hence only articles attached to an issue is effectively included in the corpus. 

Metadata such as author, date, and tags have been retrieved from the article page itself. Number of the issue is obtained based on the archive page where link to the given page was found. 

## License information

At the time contents were retrieved, the footer of zavtra.ru made clear that all contents are available under a Creative Commons license:

> Все материалы сайта доступны по лицензии: [Creative Commons Attribution 4.0 International][https://creativecommons.org/licenses/by/4.0/deed.ru)

The contents of this dataset - “zavtra.ru_ru_2024” - are distributed within the remits of this license. To the extent that it is possible, the corpus itself is also distributed by its creator, Giorgio Comai, with the same CC-BY license, as well as under the Open Data Commons Attribution license (ODC-BY).


```{r corpus_original_df}

corpus_original_df <- cas_read_db_contents_data() |> 
  dplyr::collect()

corpus_df <- corpus_original_df
```



## Dataset cleaning and reordering

The following steps are conducted on the original dataset before exporting:

- introduce an id, based on the row number after reordering for issue number; this is used for reference, and does not necessarily represent order of publication
- introduce a `doc_id` column (composed of the website base url, the language of the dataset, and the `id`) and set this as the first column of the dataset


```{r cleaning}
corpus_df <- corpus_original_df

corpus_pre_df <- corpus_df 

## ensure dates always present
corpus_df <- corpus_df |> 
  dplyr::filter(is.na(date)==FALSE) 
  
check <- assertthat::assert_that(nrow(corpus_original_df)==nrow(corpus_df), 
                        msg = "rows dropped due to missing dates")

## close dataset at end date
corpus_df <- corpus_df |> 
  dplyr::filter(date<=end_date) 

## add id 

corpus_df <- corpus_df |> 
  dplyr::arrange(as.numeric(issue_number)) |> 
  dplyr::mutate(id = dplyr::row_number())


corpus_df <- corpus_df |> 
  dplyr::rowwise() |> 
  dplyr::mutate(doc_id = stringr::str_c(website_name, "_", id)) |> 
  dplyr::ungroup() |> 
  dplyr::relocate(doc_id, text, title, date, datetime) |> 
  dplyr::relocate(id, url, .after = dplyr::last_col())

check <- assertthat::assert_that(nrow(corpus_df) == nrow(corpus_df |> dplyr::distinct(doc_id)),
                                 msg = "duplicated doc_id")
```


```{r piggyback, eval = FALSE}

corpus_path <- fs::path(fs::path_home_r(), 
                      "R",
                      "castarter_2024",
                      "corpora")

fs::dir_create(corpus_path)

csv_release_file <- fs::path(corpus_path, 
                         stringr::str_c(corpus_name, ".csv.gz"))

corpus_df |> 
  readr::write_csv(file = csv_release_file)


piggyback::pb_new_release(repo = "giocomai/tadadit",
               tag = corpus_name,
               body = summary_stats_text)

piggyback::pb_upload(file = csv_release_file,
          repo = "giocomai/tadadit",
          tag = corpus_name)

ods_file <- fs::path(corpus_path, 
                         stringr::str_c(path = corpus_name, ".ods"))
                      
readODS::write_ods(x = corpus_df, path = ods_file)

piggyback::pb_upload(file = ods_file,
          repo = "giocomai/tadadit",
          tag = corpus_name)


rds_file <- fs::path(corpus_path, 
                         stringr::str_c(path = corpus_name, ".rds"))
                 
saveRDS(object = corpus_df, file = rds_file)

piggyback::pb_upload(file = rds_file,
          repo = "giocomai/tadadit",
          tag = corpus_name)

cas_write_corpus(corpus = corpus_df,
                 partition = "year",
                 tif_compliant = FALSE,
                 path = fs::path(corpus_path, corpus_name))
```


## Outputs related with this corpus

- Comai, Giorgio (2023), "Who said it first? ‘The collective West’ in Russia’s nationalist media and official statements", tadadit.xyz, 14 March 2023,  [https://tadadit.xyz/posts/2023-03-who-says-it-first-nationalist-media-kremlin/](https://tadadit.xyz/posts/2023-03-who-says-it-first-nationalist-media-kremlin/)