---
title: "Russian institutions 2024"
listing:
  sort: "title asc"
  type: table
  image-align: right
  categories: true
  sort-ui: true
  filter-ui: true
  feed: true  
  fields: [title, description, categories]
editor: source
---

This is a collection of textual datasets based on websites of Russian institutions.

This is a stable release.

- all datasets do not include materials publised after 31 December 2023
- download urls and links to metadata pages are expected to remain available
- a formal release in an established repository is forthcoming - relevant links will be added here
- context and use cases will be described in a dedicated book chapter [forthcoming] 

The name of each corpus is composed of the bare domain name, a two letter code of the main language of the contents, and the year of release of the dataset, separated by an underscore, e.g. `kremlin.ru_ru_2024`.

```{r echo=FALSE, eval = TRUE, message=FALSE, warning=FALSE}
library("piggyback")
options(piggyback.verbose = FALSE)
base_folder <- fs::dir_create(fs::path(fs::path_home_r(), "R", "ru_institutions_2024"))

get_corpus <- function(corpus_name) {
  pb_download(dest = base_folder, 
            repo = "giocomai/tadadit",
            tag = corpus_name, 
            file = stringr::str_c(corpus_name, ".csv.gz", collapse = ""))
  invisible(fs::path(base_folder, stringr::str_c(corpus_name, ".csv.gz", collapse = "")))
}

```

## Summary statistics

```{r echo=FALSE, message=FALSE, warning=FALSE}
#| column: page

available_df <- tibble::tribble(
  ~institution, ~corpus_name, 
  "Russia's president", "kremlin.ru_en_2024", 
  "Russia's president", "kremlin.ru_ru_2024",
  "Russia's MFA", "mid.ru_ru_2024",
  "Russia's MFA", "mid.ru_en_2024",
  "Russia's government (archived version)", "archive.government.gov.ru_ru_2024",
  "Russia's prime minister (archived version)", "archive.premier.gov.ru_ru_2024"
  )

summary_stats_df <- purrr::map(
  .x = purrr::transpose(available_df),
  .f = \(x) {

    corpus_df <- invisible(readr::read_csv(file = get_corpus(corpus_name = x[["corpus_name"]])))
    
    earliest <- min(corpus_df[["date"]])
    
    total <- nrow(corpus_df)
    
    tibble::tibble(
      institution = x[["institution"]],
      website = stringr::str_remove(string = x[["corpus_name"]],
                                   pattern = "_[[:alpha:]]{2}_[[:digit:]]{4}$"), 
                   language = stringr::str_remove(string = x[["corpus_name"]],
                                   pattern = "_[[:digit:]]{4}$") |> 
      stringr::str_extract(pattern = "[[:alpha:]]{2}$"), 
      `start date` = min(corpus_df[["date"]]), 
      `end date` = max(corpus_df[["date"]]), 
      n_items = nrow(corpus_df)
      )
  }) |> 
  purrr::list_rbind()

summary_stats_df |> 
  knitr::kable(format.args = list(big.mark = " "))
```

## List of available datasets